An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-18 VLDB2026/main.tex
Update main.tex

	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluate the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability. Notably, the previously discussed datasets primarily relied on synthetic attributes for experimentation. Therefore, we additionally incorporated two datasets containing real attributes for a more comprehensive evaluation:}

	\textcolor{violet}{YT-Audio-Real: We utilized the URLs provided by the YouTube8M dataset to crawl the corresponding video category IDs and view counts as their real attributes.}

	\textcolor{violet}{WIT-Real: For this dataset, we encoded the page\_title field into vectors using the \texttt{clip-vit-base-patch32} model, and used the language type and the length of the context\_page\_description field as real attributes.}
%	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.

>>>>

	\textcolor{violet}{In addition to the aforementioned datasets, we further evaluated the performance of various algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage} and the large-scale dataset Deep100M to validate the algorithm generalization capability. Specifically, the Text2Image dataset comprises two versions: the original version contains 1 million image embeddings as the base dataset and uses 10 thousand text embeddings as the query set; the Text2Image-Mix version is composed of 0.5 million image embeddings and 0.5 million text embeddings as the base dataset, with a query set of 5 thousand image embeddings and 5 thousand text embeddings.}

	\textcolor{violet}{Given that the preceding datasets primarily utilized synthetic attributes, we additionally introduced two datasets containing real attributes for a more comprehensive evaluation: the YT-Audio-Real dataset leverages URLs provided by the YouTube8M dataset to crawl corresponding video category IDs and view counts as its real attributes; whereas for the WIT-Real dataset, we encoded the \texttt{page\_title} field into vectors using the \texttt{clip-vit-base-patch32} model, and used the language type and the length of the \texttt{context\_page\_description} field as real attributes.}

%	In addition, we evaluate the performance of different algorithms on the Out-of-Distribution (OOD) dataset Text2Image~\cite{texttoimage}.
